Practical Challenges with Web Service Evolution:\\A Review of Literature and Current Industry Practices

### 2013-05-31 paper.tex
et al. (dot added)

XXXXX WHAT FOLLOWS XXXXX

@@

\subsection{Systematic Literature Review} % (fold)
\label{sub:systematic_literature_review}
Kitchenham et al defines systematic review as follows \cite{kitchenham2007guidelines}:

@@

\subsubsection{Why Do Web Services Evolve?} % (fold)
\label{sub:why_do_web_services_change}
In this section, we have discussed the drivers behind web service evolution from the related literature. To begin with, in \cite{treiber2009analyzing} Treiber et al provided a list of changes related to web services with their interdependencies. To identify the source and impact of a change, they categorized the stakeholders into four roles:

@@

Borovskiy et al identified some drivers behind web service evolution from the perspective of an enterprise, where both the web service consumer and publisher may be part of the same organization \cite{borovskiy2008evolution}. In this regard, they categorized two classes of drivers behind the evolution of web services as follows:

@@

Using a similar approach but instead of arbitrary custom tags to extend the schema, Fang et al provides a concrete list of six XML nodes to create a version-aware service model for SOAP web services [A Version-aware Approach for Web Service Directory]. They introduced extensions to WSDL and UDDI to tackle evolving web services. These extensions are composed of six XML nodes: 1) version name, 2 ) version description, 3) startTime of the version, 4) endTime of the version, 5) alias such as (new, current etc) of the version name and, 6) original version that preceded it.

@@

In \cite{leitner2008end} Leitner et al provided an alternative approach to transparently handle multiple versions of SOAP web services using their framework called VRESCo. At it’s core, VRESCo builds a graph of the versions showing predecessor relations as follows:

XXXXX VRESCO IMAGE XXXXX

@@

In addition to the protocol level evolution support for SOAP web services, Mangler et al showed a solution for RESTful web services in \cite{mangler2010origin}. They introduced a description language called RIDDL for RESTful web services to support service composition and evolution.

@@

Kaminski et al presented a design technique for evolving web services from the perspective of the source code implementation \cite{kaminski2006design}. They identified some key requirements for their design such as: \textbf{a) backward compatibility, b) common data store, c) no code duplication, d) untangled versions, e) unconstrained evolution, and f) a visible mechanism}. To summarize, the design aimed to allow for web service evolution while staying compatible with the existing clients without introducing duplication in the code or in the data store in a transparent manner.

With these requirements laid out, they proposed a design technique called ``Chain of Adapters'' for the implementation of evolving web services. The following figure shows a high level view of the design:

XXXX Chain of Adapters XXXXX

Source: \cite{kaminski2006design}

@@

In \cite{le2008synchronizing} Zou et al presents a technique to generate consumer specific changelogs for evolving SOAP web services. When a new version of a web service is published, it typically accompanies a custom formatted, often HTML based, documentation of it’s methods and parameters. For existing consumers, this may require a significant effort to identify the impacts of the new version specific to their usage by looking at the potentially large documentation. To address this problem, the authors suggested creating customized release notes for each consumer based on their usage pattern in the following steps:

@@

Aversano et al provided an alternate approach to communicate changes in SOAP web services using a graphical way in \cite{aversano2005visualizing}. To construct the graphical representation, the authors extracted meta information about methods and parameters for SOAP web services from the WSDL files. This meta information is then presented in a graph to visualize the service with its methods and parameters. The graph can be used to visually communicate the similarities and differences among the subsequent versions of the same service.

>>>>

The remainder of this paper is organized as follows: in the next section we discuss the motivation behind this research followed by our research questions. Then, we discuss the research method and findings in Sections \ref{sec:research_method} and \ref{sec:research_findings} respectively. Finally, we present the key challenges and future work opportunities with evolving web services in Section \ref{sec:discussion}.

@@

\subsection{Systematic Literature Review} % (fold)
\label{sub:systematic_literature_review}
Kitchenham et al. defines systematic review as follows \cite{kitchenham2007guidelines}:

@@

\subsubsection{Why Do Web Services Evolve?} % (fold)
\label{sub:why_do_web_services_change}
In this section, we have discussed the drivers behind web service evolution from the related literature. To begin with, in \cite{treiber2009analyzing} Treiber et al. provided a list of changes related to web services with their interdependencies. To identify the source and impact of a change, they categorized the stakeholders into four roles:

@@

Borovskiy et al. identified some drivers behind web service evolution from the perspective of an enterprise, where both the web service consumer and publisher may be part of the same organization \cite{borovskiy2008evolution}. In this regard, they categorized two classes of drivers behind the evolution of web services as follows:

@@

Using a similar approach but instead of arbitrary custom tags to extend the schema, Fang et al. provides a concrete list of six XML nodes to create a version-aware service model for SOAP web services [A Version-aware Approach for Web Service Directory]. They introduced extensions to WSDL and UDDI to tackle evolving web services. These extensions are composed of six XML nodes: 1) version name, 2 ) version description, 3) startTime of the version, 4) endTime of the version, 5) alias such as (new, current etc) of the version name and, 6) original version that preceded it.

@@

In \cite{leitner2008end} Leitner et al. provided an alternative approach to transparently handle multiple versions of SOAP web services using their framework called VRESCo. At it’s core, VRESCo builds a graph of the versions showing predecessor relations as shown in Figure \ref{fig:vresco}:

\begin{figure*}[bt]
  \centering
  \includegraphics[width=\textwidth]{vresco.png}
    \caption{VRESCo Service Version Graph, source: \cite{leitner2008end}}
  \label{fig:vresco}
\end{figure*}

@@

In addition to the protocol level evolution support for SOAP web services, Mangler et al. showed a solution for RESTful web services in \cite{mangler2010origin}. They introduced a description language called RIDDL for RESTful web services to support service composition and evolution.

@@

Kaminski et al. presented a design technique for evolving web services from the perspective of the source code implementation \cite{kaminski2006design}. They identified some key requirements for their design such as: \textbf{a) backward compatibility, b) common data store, c) no code duplication, d) untangled versions, e) unconstrained evolution, and f) a visible mechanism}. To summarize, the design aimed to allow for web service evolution while staying compatible with the existing clients without introducing duplication in the code or in the data store in a transparent manner.

With these requirements laid out, they proposed a design technique called ``Chain of Adapters'' for the implementation of evolving web services. Figure \ref{fig:chain_of_adapters} shows a high level view of the design.

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{chain_of_adapters.png}
    \caption{Chain of Adapters structure, source: \cite{kaminski2006design}}
  \label{fig:chain_of_adapters}
\end{figure*}

@@

In \cite{le2008synchronizing} Zou et al. presents a technique to generate consumer specific changelogs for evolving SOAP web services. When a new version of a web service is published, it typically accompanies a custom formatted, often HTML based, documentation of it’s methods and parameters. For existing consumers, this may require a significant effort to identify the impacts of the new version specific to their usage by looking at the potentially large documentation. To address this problem, the authors suggested creating customized release notes for each consumer based on their usage pattern in the following steps:

@@

Aversano et al. provided an alternate approach to communicate changes in SOAP web services using a graphical way in \cite{aversano2005visualizing}. To construct the graphical representation, the authors extracted meta information about methods and parameters for SOAP web services from the WSDL files. This meta information is then presented in a graph to visualize the service with its methods and parameters. The graph can be used to visually communicate the similarities and differences among the subsequent versions of the same service.
